Seniority and Hierarchy Configuration Interaction for Radicals and \\ Excited States

### 2023-08-28 Manuscript/Cover_Letter/Cover_Letter.tex
more refs
capital letters

\justifying
Please find enclosed our manuscript entitled \textit{``Seniority and hierarchy configuration interaction for radicals and excited states''}, 
which we would like you to consider as a Regular Article to the \textit{Journal of Chemical Theory and Computation}.
This contribution has never been submitted in total nor in parts to any other journal, and has been seen and approved by all authors.

>>>>

\justifying
Please find enclosed our manuscript entitled \textit{``Seniority and Hierarchy Configuration Interaction for Radicals and Excited States''}, 
which we would like you to consider as a Regular Article to the \textit{Journal of Chemical Theory and Computation}.
This contribution has never been submitted in total nor in parts to any other journal, and has been seen and approved by all authors.
